Rarefy Timeseries

### 2024-05-30 analysis/02_rarefy_timeseries.Rmd
Accidentally erased at some point

##	Get trait filtered data, rename columns to jive with the rest of the script
bt_traitfiltered <- bt_traitfiltered
  rename_with(toupper) %>%
  rename(Species = SPECIES, StudyMethod = STUDYMETHOD, ObsEventID = OBSEVENTID,
         rarefyID = RAREFYID, cell = CELL, Abundance = ABUNDANCE, Biomass = BIOMASS)

>>>>

##	Get trait filtered data, rename columns to jive with the rest of the script
bt_traitfiltered <- bt_traitfiltered %>%
  rename_with(toupper) %>%
  rename(Species = SPECIES, StudyMethod = STUDYMETHOD, ObsEventID = OBSEVENTID,
         rarefyID = RAREFYID, cell = CELL, Abundance = ABUNDANCE, Biomass = BIOMASS)
